Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-15 WRITEUP/ms.tex
minor edits

% This is the messy stage
\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated.
Colorbar on the right shows the mean
H$_2$ number density, weighted by gas mass. Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MCC}\AP{see \Fig{MMCidentification} for an alternative version}}
\end{figure*}

% Add a figure that shows \flower in "disky" stage. We are interested in exploring whether the MCC properties are dependent on the disk properties.
% In other words, if the nature of the MCCs we are identifying are large chucks of arms/disk in \flower, then its dynamics that we are deriving will be dominated by
% large-scale shear.
\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_0.53}.pdf}
  \\ [-2.7em]
  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_6.81}.pdf}
  \\ [-2.7em]
  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_18.96}.pdf}
\caption{
Same as \Fig{MCC} for the quiescent phase of \flower, when the galaxy is supported by rotation.
\label{fig:MCC28} \AP{see \Fig{MMCidentification} for an alternative version}}
\end{figure*}

@@

  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
\caption{\AP{proposed alternative to substitute \Fig{MCC} and \Fig{MCC28}; if adopted, label with the phase should be included in the first row}
\label{fig:MMCidentification}
}
\end{figure*}

@@

To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}). Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
stellar-to-gas mass ratio of $\simeq$\,50--100. 
The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
in the accreting and quiescent phases of \flower.
The accreting phase of \flower displays a disturbed morphology (\Fig{MCC}) while the 
quiescent phase displays a disk-like morphology (\Fig{MCC28}).
Excluding the structure corresponding to the molecular disk, the 
velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and quiescent phase (bottom) of \flower.
%
The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
%
Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}). A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs. On the other hand, the  remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.

@@

\AP{the following should be removed if the corresponding point in the main text is commented out (as it has been now)}
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}. This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.

>>>>

@@

  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
its quiescent phase, which is rotation-dominated (right two columns).
Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
in the quiescent phase.
Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
\AP{label with the phase should be included in the first row}
\label{fig:MCC}
}
\end{figure*}

@@

To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}). Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections so that the identification can be more easily appreciated.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.

@@

The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
stellar-to-gas mass ratio of $\simeq$\,50--100. 
The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
in the accreting and quiescent phases of \flower.
The accreting phase of \flower displays a disturbed morphology, whereas the 
quiescent phase displays a disk-like morphology (\Fig{MCC}).
Excluding the structure corresponding to the molecular disk, the 
velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and quiescent phase (bottom) of \flower.
%
The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC}).
%
Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs. On the other hand, the  remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.

@@

The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}. This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.
